---
title: "Yx2510_p8105_hw5"
author: "Yi Xiao"
date: "02/11/2018"
output: github_document
---
Load the packages 
```{r}
library(tidyverse)
```
## Problem one:
Read the file:
1. Start with a dataframe containing all file names
```{r}

name = list.files(path = "./data", full.names = TRUE) %>% 
        as.data.frame()
        colnames(name) = "subject"

```
2. Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
```{r}
data =  map(as.character(name$subject), read_csv) 
data_combi = data[[1]]
for (i in 2:20) {
data_combi = rbind(data_combi, data[[i]])
}
my_data = cbind(name, data_combi)
```

3. Tidy the data
```{r}
 my_tidy_data = my_data %>%
        gather(key = week, value = value, week_1 : week_8) %>%
        mutate(subject = str_replace(subject, "./data/", ""),
               subject = str_replace(subject, ".csv", ""),
               week = str_replace(week, "week_", "")) %>%
        separate(subject, into = c("group", "subject_id"), sep = "_")

        
```

4. Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
my_tidy_data %>%
        ggplot(aes(x = as.numeric(week), y = value)) +
        facet_grid(~ as.factor(group)) +
        geom_line(aes(color = subject_id)) +
        labs(x = "Week",
             y = "Value",
             title = "Value of each subject over 8 weeks by group") +
        theme(legend.position = "bottom")
        
```

Comment: The week-one value ranged from 0.0 to 2.5. A slightly wider range was observed in the experiment group which fell between -1.0 to 3.725. However, the value in the control arm fluctuated arond this range for the following 8 weeks. Meanwhile, an overall increasing trend can be observed for the experimental group.